Inferring Graphics Programs from Images

### 2017-05-09 paper.tex
added figures back in

How could an agent go from noisy,
high-dimensional perceptual input to a symbolic, abstract object, like
a computer program?  Here we consider this problem within the context
of \emph{graphics program synthesis}.  We develop an approach for
converting natural images, such as hand drawings, into executable
source code for drawing the original image.

@@

High dimensional perceptual input is ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions. Our hypothesis is that the execution trace of the
program is better aligned with the perceptual input, and that the
trace can act as a kind of bridge between perception and programs. We
test this hypothesis by developing a model that learns to map from an
image to the execution trace of the graphics program that drew it.
With the execution trace in hand, we can bring to bear techniques from
the program synthesis community to recover the latent graphics program.

@@

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR.

@@

\section{Contributions}

We see this system as a first step towards more powerful graphics
program synthesizers.  We look forward to, in the near future, being
able to hand-draw our figures and automatically convert them into
publication-quality \LaTeX code.

\pagebreak

>>>>

\textbf{Comment for reader: this paragraph is a little grandiose and goes
  beyond what we've actually done. But these are the kinds of things
  that motivate the work, and I think that in some form these ideas
  should be in the introduction or the conclusion.} How could an agent go from noisy,
high-dimensional perceptual input to a symbolic, abstract object, like
a computer program?  Here we consider this problem within the context
of \emph{graphics program synthesis}.  We develop an approach for
converting natural images, such as hand drawings, into executable
source code for drawing the original image.
\remark{The use of `graphics programs / visual programs' in the paper title, title of this section, and the body of this section feels too broad. `Graphics program' could conjur a lot of different ideas (esp. 3D graphics); don't want to set the reader up to expect one thing and then be disappointed that what you've done isn't that. You bring up diagram-drawing later in the intro; I think it should be made clear sooner (and certainly mentioned explicitly in the abstract, when you get around to writing that).}

@@

High dimensional perceptual input is ill matched to the abstract
semantics of a programming language. But programs with constructs like
recursion or iteration produce a simpler \emph{execution trace} of
primitive actions. Our hypothesis is that the execution trace of the
program is better aligned with the perceptual input, and that the
trace can act as a kind of bridge between perception and programs. We
test this hypothesis by developing a model that learns to map from an
image to the execution trace of the graphics program that drew it.
With the execution trace in hand, we can bring to bear techniques from
the program synthesis community to recover the latent graphics program.
\remark{This is an \emph{excellent} explanation! I would add maybe one more sentence / citation to elaborate on what you mean by `techniques from the program synthesis community', as this will be an unfamiliar concept to some readers, I imagine.}

@@

We train the network by sampling execution traces $T$ and target
images $I$ for randomly generated scenes, and maximizing
(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
architecture being recurrent, training is fully supervised. In a
sense, this model is like an autoregressive variant of AIR.
\remark{I like that you make this connection, but it could be made more precisely. Specifically, (1) the architecture isn't \emph{really} recurrent (it uses no hidden state cells), so it'd be good to use a different term or drop this part of the point: (2) training of recurrent nets is also typically fully-supervised (Most RNNs lack latent variables per timestep)---if you're thinking about AIR specifically, maybe just say that, and (3) it's like an autogressive AIR \emph{without attention}.}
\remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}

@@
